---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PopEpi.R

### R Functions for the Pop Epi Team

The PopEpi.R package contains assorted functions that help the PSB Pop Epi team with common data wrangling tasks, or functions which are designed to speed up and ease the work done by the PSB Pop Epi Team, or that may otherwise be useful.

## Installation

You can install the development version of PopEpi.R from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("shellylac/PopEpi.R")
```

## Details

Currently this package only contains 2 functions:

1.  `create_popepi_project()` which creates and open an R project directory that has relevant sub-directories and is git-enabled and has a basic README.md template,

2.  `%nin%` - a simple utility tool that is basically gives the opposite of the base R `%in%` function (which uses `match()`)

It is envisioned that all team members will contribute to making this package an even more amazing resource - by adding more functions!

To get up to speed on how to contribute functions for this package I recommend these resources:

-   [The R Packages Online Manual](https://r-pkgs.org/) by Hadley Wickam and Jennifer Bryan

-   [This tutorial](https://ourcodingclub.github.io/tutorials/writing-r-package/) from Our Coding Club

-   [Functions Chapter](https://r4ds.had.co.nz/functions.html) from R for Data Science by Hadley Wickam and Garrett Grolemund

-   [Code Testing](https://stirlingcodingclub.github.io/code_testing/testing_notes.html) by Brad Duthie

All functions contributed to this package must serve a single and specific purpose, have gone through code review by another team member, and must be well documented, provide useful examples, and be robustly tested.

## Example usage

```{r example}
library(PopEpi.R)

### set up a bespoke git-enabled R project directory
# create_popepi_project(path = "C:/Users/pathto/my_analysis")

### get help on a package function
# ?create_popepi_project
```

## A note on this README file

This README.md file is constructed by renderering the `README.Rmd` and this should be done regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

As this README file is built from and Rmd file we could embed r code chunks or plots. If you want the plots to display in the README file then don't forget to commit and push the resulting figure files (see the path for figures in the knitr options above), so they display on GitHub.

<!-- This is an added comment to test Github push functionality -->
